\section{Results}

Table~\ref{tab:overall} should be interpreted as summarizing the current BEACON-semantics sweep rather than the older 400-episode benchmark language. In the present evaluation, the directly compared planners are Bug, Bug2, D* Lite, and BEACON. D* Lite and BEACON both achieve perfect success on the recorded sweep, while Bug and Bug2 are substantially less reliable. However, BEACON does not reduce traversal energy relative to D* Lite in this sweep: D* Lite records a mean traversal energy of 24.547, whereas BEACON records 25.252. Because no pushes were executed in the main sweep, the measured energy is dominated by traversal effort rather than manipulation work.

This means the strongest result in the current sweep is robustness, not lower energy expenditure. BEACON matches D* Lite on success but uses more steps on average and slightly higher traversal energy, while Bug and Bug2 often terminate early and therefore show shorter paths and lower energy for the wrong reason. A tuned BEACON pass with a finer planner step and less conservative obstacle blocking reduces BEACON's baseline mean traversal energy to 24.699 while preserving 100\% success, but it still does not outperform D* Lite on the main sweep.

To better evaluate BEACON's intended push-versus-reroute behavior, a separate push-heavy benchmark harness was added with corridor-style scenes containing movable plugs and long rigid detours. That auxiliary benchmark is designed to activate the force--energy model in cases where manipulation is genuinely competitive with rerouting. Accordingly, the current paper figures should describe the existing semantics sweep honestly: BEACON matches D* Lite in success, but it does not reduce traversal energy in this sweep.
